\documentclass[10pt, conference, compsocconf]{IEEEtran}
\usepackage{url}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{setspace}
\usepackage{multirow}
\usepackage{array}
\usepackage{graphics}
\usepackage{comment}
\usepackage{url}
\usepackage{color}

% correct bad hyphenation here
\hyphenation{}


\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Towards Minimizing the Required Bandwidth for Mobile Web Browsing}

% author names and affiliations
% use a multiple column layout for up to two different
% affiliations

\author{\IEEEauthorblockN{Madhuvanthi Jayakumar, Marcela Melara, and Nayden Nedev}
\IEEEauthorblockA{Princeton University\\
\{jmadhu, melara, nnedev\}@cs.princeton.edu}}

% make the title area
\maketitle

\begin{abstract}
%The number of smartphones has been increasing in a very fast pace over the last several 
%years. With this speed, it is quite likely that they will dominate the market in the very 
%near future. As a result, the amount of mobile Web traffic now takes a serious portion of 
%the total amount of Internet traffic. Moreover, it is expected to grow exponentially with 
%every subsequent year. These facts put new challenges in the ways mobile networks are designed 
%and built. New methods for alleviation of the amount of transmitted mobile web traffic data
%should be found. 

%In this paper, we propose a novel technique for reducing the needed bandwidth for mobile Web 
%browsing. It automatically identifies redundancies in mobile Web sites data and cuts the number
%of transimitted bytes. We leverage partitioning of website data into chunks and fingerprinting them
%for efficient retrieval from a cache. The only addition to the network that our method requires 
%is a dedicated proxy server which serves as a cache. We implement our techniques in a sophisticated 
%simulator and evaluate their effectiveness on a number of popular websites. Our empirical results 
%show that, with an appropriate tuning of all system components, the needed bandwidth can be reduced 
%to less than 10\% in some cases.

The number of smartphones has been increasing at a very fast pace over the last several 
years. At this rate, it is quite likely that mobile web traffic will take a serious portion of the global Internet traffic in the very near future. However, the improvement of mobile web access technology has been known to lag behind the current growth: we face issues such as limited bandwidth and computational power and high latency. Additionally, users have financial incentives to use their limited data plan effectively.
These facts motivate new ways of designing and building mobile web access technologies and networks. Specifically, new methods for reducing mobile web traffic and for utilizing the mobile computational and network resources more efficiently should be found.

In this paper, we propose a novel technique for reducing the needed bandwidth for mobile web browsing. It automatically identifies redundancies in mobile website data to reduce the number of transmitted bytes. We leverage the standard deduplication techniques of partitioning website data into chunks and fingerprinting them
for redundancy detection and efficient retrieval from a cache. The only additions to the current mobile browsing framework that our method requires is a dedicated proxy server and the installation of a mobile proxy-client. We implement our techniques in a sophisticated  simulator and evaluate their effectiveness on a number of popular websites. Our empirical results show that, with an appropriate tuning of all system components, the needed bandwidth can be reduced to less than 10\% in some cases.
\end{abstract}

%\begin{IEEEkeywords}
%component; formatting; style; styling;
%\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

%\category{}{}{}

\input{intro}
\input{rel_work}
\input{design}
\input{protocol}
\input{implementation}
\input{eval}
\input{discussion}
\input{conclusion}

% use section* for acknowledgement
\section*{Acknowledgments}
We would like to thank.. 

\bibliographystyle{abbrv}
\bibliography{bigdata}

\end{document}
